---
toc: true
toc-depth: 3
toc-location: left
number-sections: true
highlight-style: pygments
format:
  html:
    df-print: kable
    code-fold: show
    code-tools: false
    css: styles.css
    link-external-icon: true
    link-external-newwindow: true  
editor_options: 
  chunk_output_type: console
---

 

```{r, echo= FALSE}

knitr::opts_chunk$set(eval = FALSE)

```

1)  Install or update R on the computer you will use during the course (<https://cran.r-project.org>). I assume that you already have it installed, but try to update it if you have a R version \< 4.0.0. You can find which R version you have by running this in the R console:

```{r}

version$version.string

```

2)  Update all R packages if you already had R installed (`r emo::ji("warning")` this step can take a long time to run `r emo::ji("warning")`):

```{r}

update.packages(ask = FALSE)
```

3)  Install or update the *RStudio* interface (<https://www.rstudio.com/products/rstudio/download/>, choose the free version). Optional but advised.

4)  Make a directory called "OTS_REU_OS_2024", this will be your working directory for the course.

5)  Open *RStudio* and select the tab "Tools" then "Global Options" (last option). Select the "Code" option, then select the box for "Soft-wrap R source files".

6)  Also in *RStudio*: Select the "Pane Layout" option and move "Source" to the top left pane and "Console" to the top right pane. For those of you unfamiliar with *RStudio*, the source is your script, where you save code in a physical file (usually .R script) and the console prints the output of the code you run from the source. You can write code in the console, but it will not be saved in a physical file. This layout allocates more screen space to the most useful panes. Hit "Apply" and "Ok".

7)  Also in *RStudio*: Go back up to the "File" tab and select "New Project", then select the "OTS_REU_OS_2024" directory.

8)  Now in the R console in *RStudio*: Run the following code to install some R packages (remove the packages first if you have them installed already).

```{r, eval = FALSE}

# install package to install packages
install.packages("sketchy") 

# load sketchy
library(sketchy)

# install packages
load_packages(
  packages = c(
    "rgbif",
    "rmarkdown",
    "knitr",
    "kableExtra",
    "rmdformats",
    "revealjs",
    "rticles",
    "tufte",
    "ggplot2",
    "viridis",
    "taxize",
    github = "hadley/emo",
    github = "benmarwick/rrtools",
    github = "CrumpLab/vertical",
    github = "crsh/papaja"
  )
)


```

8)  Install git (<https://git-scm.com/book/en/v2/Getting-Started-Installing-Git>)

9)  Create a github account (<https://github.com/signup>)

10) Install *Github Desktop* (<https://docs.github.com/en/desktop/installing-and-authenticating-to-github-desktop/installing-github-desktop>)

11) On *Github Desktop* log in into your github account using github

12) Register yourself in *Rpubs* (https://rpubs.com/)

::: {.alert .alert-warning}
**A few tips to make sure you will take full advantage of the course**:

-   Ideally, read the materials ahead of time (I know! it's time consuming)
-   Make sure you have anything you need before the start of the class
-   Be ready a few minutes before the start of the class
-   Try to focus as much as possible in the course, close other programs or unnecessary internet browser tabs (i.e. instagram, twitter, etc). This will also make the computer more efficient (less likely to get slow)
-   Comment your code
:::
